% =========================================================================
% Section II: Related Work
% Governing docs: paper2-uav/LIT_REVIEW.md (verified references only),
% paper/OUTLINE.md §II. Reviewer-proof prior-art sentences used verbatim
% where provided. No claims outside the claims-evidence table.
% =========================================================================

\section{Related Work}
\label{sec:related}

\subsection{Tiled Large-Scale Splatting and NeRF}
\label{sec:related-tiled}

\looseness=-1 Spatial partitioning is the accepted route to city-scale
radiance-field reconstruction, and existing pipelines resolve the
resulting seams geometrically: by hard spatial cropping of
out-of-tile primitives (VastGaussian~\cite{lin2024vastgaussian},
Sec.~4.3; CityGaussian~\cite{liu2024citygaussian}, Sec.~3.2 and its
released merge script; Kerbl \emph{et~al.}'s
hierarchy~\cite{kerbl2024hierarchical}, whose Sec.~6.3 deletes a
primitive trained by one chunk when it lies nearer another, a Voronoi
cull), by ADMM consensus whose parameter average
(Eq.~8b of DOGS~\cite{chen2024dogs}) weights position, quaternion, scale,
and opacity with uniform $1/K$ over a preassigned shared set, or by
hand-tuned inverse-distance image blending
(Block-NeRF~\cite{tancik2022blocknerf}, Sec.~4.3);
Mega-NeRF~\cite{turki2022meganerf}, drawn on here for its partitioning
scheme (and, in Sec.~\ref{sec:setup}, as the source of the Mill~19
collection), answers each query by a single nearest-centroid submodule.
In every case the merge rule is geometric and heuristic: none defines a
normalized global predictive density, none weights contributions by
posterior uncertainty, and duplicated boundary primitives are deleted,
never fused. That is workable for rasterization, which carries no
normalization constraint, but untenable for a generative model whose
output must integrate to one. Two designs are direct foils
for Sec.~\ref{sec:method}: Block-NeRF's separate appearance-matching
pass shows that models fit in isolation disagree at boundaries and
must be reconciled, and DOGS's uniform $1/K$ average ignores how much
evidence each replica holds; our merge answers both at once, exactly,
by adding prior-subtracted natural parameters on the pooled evidence.

\subsection{Bayesian Splatting}
\label{sec:related-bayes}

\looseness=-1 Jia \emph{et~al.}~\cite{jia2026bayesian} attach NIW
summaries to the standard photometric 3D Gaussian splatting (3DGS)
optimizer~\cite{kerbl2023gaussian}: pseudo-counts from an opacity--volume heuristic, the
optimizer's running center as ``observation,'' the NIW scatter
statistic held at zero;
no assignments, no E-step, no joint evidence lower bound (ELBO), and
the stick-breaking weights (Sec.~\ref{sec:model-recap}) acting purely
as a pruning schedule: summaries the authors themselves call
``optimization-driven approximations'' (their Sec.~4). That concession
motivates the opposite design, an exact conjugate generative
treatment in which responsibilities, sufficient statistics, and a
monotone ELBO are the inference itself, with Jia \emph{et~al.}\ as
precedent for image-space calibration; ours is in point/density
space. VBGS~\cite{vandemaele2024vbgs} is the closest inferential
relative: a conjugate mixture on colored points fitted by
coordinate-ascent variational inference (CAVI), but with a fixed finite
component budget and no predictive use of its posterior (rendered,
not queried as a density); its additive updates stream frames into one
fixed-capacity global model, whereas we decompose space, so capacity
adapts per tile and fits parallelize.
VBGS-SLAM~\cite{zhu2026vbgsslam} propagates camera-pose uncertainty for
indoor tracking, a different quantity from the map posterior used
here. None of these systems addresses tiling, overlap mass, or
model-order semantics. The DP-Splat
model, its stick-breaking prior, and its CAVI and stochastic
variational inference (SVI) are from
our prior work~\cite{dong2026dpsplat}; this paper contributes the tiled
inference, the exact merge, the stitched predictive, and the aerial
evaluation.

\subsection{3D Gaussian Splatting for Aerial Mapping}
\label{sec:related-aerial}

\looseness=-1 Partitioned aerial 3DGS pipelines (Yan
\emph{et~al.}~\cite{yan2025aerial}; Ortho-3DGS~\cite{ortho3dgs2025};
ULSR-GS~\cite{ulsrgs2024};
ARSGaussian~\cite{arsgaussian2026};
Horizon-GS~\cite{horizongs2025}) establish tiling as the accepted route
to large scenes but handle boundaries with engineering heuristics
(auxiliary supervision, view assignment) and leave component counts
uninterpreted; benchmark studies (Atik~\cite{atik2025benchmark};
Fadilah \emph{et~al.}~\cite{fadilah2026benchmark}, who find geometric
accuracy uncorrelated with rendering quality, and whose ``3DGS-MCMC''
baseline is a densification sampler, not posterior inference) quantify
error only post hoc against a reference cloud. None performs Bayesian
inference, produces a predictive density, or attaches calibrated
uncertainty to the map itself. TreeDGS~\cite{treedgs2026} reweights
primitives by an opacity-derived reliability score, a concrete
downstream consumer of the per-component uncertainty our posterior
provides in closed form; GU-GS~\cite{ding2026gugs} realizes
``uncertainty'' as a learned mask on the training loss, with no
probabilistic semantics; and PRIMU~\cite{gottwald2025primu} predicts
per-Gaussian uncertainty with post hoc features and a per-scene
learned regressor, setting the evaluation vocabulary (area under the
sparsification error curve, AUSE; error--uncertainty
correlation) we adopt. Neither of the latter two
reports calibration, the property we evaluate directly via interval
coverage.

\subsection{Uncertainty Evaluation, Distributed Nonparametric
Inference, and Active View Selection}
\label{sec:related-eval}

\looseness=-1 Our evaluation protocol assembles established instruments:
sparsification analysis and AUSE from Ilg
\emph{et~al.}~\cite{ilg2018uncertainty}, the area-under-random-gain
metric (AURG)
of Poggi \emph{et~al.}~\cite{poggi2020uncertainty}, and, for change
detection, the M3C2 distance measure~\cite{lague2013m3c2} with the
error-propagated level of detection of
M3C2-EP~\cite{winiwarter2021m3c2ep}, which targets the pitfall
(conflating surface roughness with positional uncertainty) that our
posterior-mean covariance construction likewise avoids by design
(Sec.~\ref{sec:setup:metrics}); Huang and Qin~\cite{huang2025uncertainty}
provide the plane-fit reference-based error convention our
sparsification analysis adopts on H3D
(Sec.~\ref{sec:setup:metrics}). The
merge machinery of Sec.~\ref{sec:method} is likewise adapted, not
invented: the closed-form merge-ratio score appears in memoized
variational inference~\cite{hughes2013memoized},
partition-probability-thresholded component matching in streaming
distributed Bayesian-nonparametric
inference~\cite{campbell2015streaming}, Hungarian parameter matching in
model aggregation~\cite{yurochkin2019spahm}, precision-weighted
combination in consensus Monte Carlo~\cite{scott2016consensus}, and the
concentration bookkeeping $\sum_t \alpha_t = \alpha$ that motivates
interpreting the merged union against a single global DP in Williamson
\emph{et al.}~\cite{williamson2013parallel} (Thm.~1); kernel
stick-breaking~\cite{dunson2008kernel} anchors the tiling: in the
compact-kernel limit, spatially localized mixtures reduce to
independent per-region DPs, the regime our tiles approximate.
Finally, uncertainty-driven view selection for splatting
(GAVIS~\cite{xue2026gavis}, FisherRF~\cite{jiang2024fisherrf},
ActiveSplat~\cite{li2025activesplat}, GauSS-MI~\cite{xie2025gaussmi}) is
sequential, GPU-rasterized, photometric, and room-scale; our re-flight
problem is batch, tile-level acquisition
ranking from rasterization-free closed-form posterior scores, evaluated
by held-out predictive density on a held-back image block's
triangulated points. GAVIS argues that parameter-space
uncertainty underestimates unseen regions; a nonparametric predictive,
whose prior reverts to a fat-tailed, low-capacity regime where data are
absent, is a natural response, and we test it directly.
